An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures

### 2021-04-29 CMPSpaper_writing/CMPSpaper_writing.Rmd
small code, dpi included in options

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "\\textwidth",
  fig.align = "center"
)
```

@@

codefigChunkHook <- function(x, options) {
  main <-  defaultChunkHook(x, options)
  before <-
    "\\vspace{1em}
\\begin{adjustbox}{valign=t}
\\begin{minipage}{.49\\textwidth}\n"
  after <-
    paste("\\vspace{1em}
\\end{minipage}
\\begin{minipage}{.49\\textwidth}",
    paste0("\\includegraphics[width=\\textwidth]{CMPSpaper_writing_files/figure-latex/",
                 options[["label"]], "-1.pdf}
\\end{minipage}
\\end{adjustbox}"),
          sep = "\n")
  ## Was a codefig option supplied in chunk header?
  ## If so, wrap code block and graphical output with needed LaTeX code.
  if (!is.null(options$codefig)) {
    main <- gsub("```","", main)
    main <- gsub("=latex","", main)
    return(sprintf("%s\n%s\n%s", before, main, after))
  } else {
    return(main)
  }
}

@@

2. **register each basis segment on the comparison signature:** 
Calculate the cross-correlation curve between a basis segment `x` and the comparison signature `y` using the function `get_ccf4(x, y, ...)`.
A position is considered "good" if it results in a peak in the cross-correlation between the basis segment and the comparison.
<!-- the cross-correlation between the basis segment and the comparison is above a pre-defined threshold.  -->
The best registration position is decided upon using a multi-peak inspection with or without different segment lengths:

@@

dframe <- comparisons %>% select(-aligned, -cmps)
```

```{r, echo=FALSE}
dframe %>% ggplot(aes(x = landB, y = landA, fill = cmps_score)) + geom_tile() + 
  scale_fill_gradient2(low = "gray80", high = "darkorange", midpoint = 6) + 
  facet_grid(bulletA ~ bulletB, labeller = "label_both") + xlab("Land B") + 
  ylab("Land A") + theme(aspect.ratio = 1) +
  geom_text(aes(label=cmps_score)) +
  theme_bw()
```

@@

\begin{figure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot3}put segment\_plot and scale\_ccf\_plot of all scales together. We are identifying five highest peaks at scale 1, three peaks at scale 2, and one peak at scale 3 since npeaks.set = c(5, 3, 1). Putting these plots together can help better understand why segment 6 is not a congruent matching profile segment. Here we can also see clearly that increasing segment length can reduce the number of false positive peaks.}
```{r segplot3, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
library(ggpubr)

ggarrange(
  plotlist = 
    unlist(seg.plot, 
           recursive = FALSE),
  ncol = 2, 
  nrow = 3)
```
\end{subfigure}
\caption{\label{fig:seg_all} some text.}
\end{figure}

>>>>

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "\\textwidth",
  fig.align = "center",
#  cache=TRUE,
  dpi = 100
)
```

@@

codefigChunkHook <- function(x, options) {
  main <-  defaultChunkHook(x, options)
  before <-
    "\\vspace{1em}
\\begin{adjustbox}{valign=t}
\\begin{minipage}{.39\\textwidth}\n"
  after <-
    paste("\\vspace{1em}
\\end{minipage}
\\begin{minipage}{.59\\textwidth}",
    paste0("\\includegraphics[width=\\textwidth]{CMPSpaper_writing_files/figure-latex/",
                 options[["label"]], "-1.pdf}
\\end{minipage}
\\end{adjustbox}"),
          sep = "\n")
  ## Was a codefig option supplied in chunk header?
  ## If so, wrap code block and graphical output with needed LaTeX code.
  if (!is.null(options$codefig)) {
    main <- gsub("```","", main)
    main <- gsub("=latex","", main)
    main <- paste0("{\\small ", main, "}")
    return(sprintf("%s\n%s\n%s", before, main, after))
  } else {
    return(main)
  }
}

@@

2. **register each basis segment on the comparison signature:** 
Calculate the cross-correlation curve between a basis segment `x` and the comparison signature `y` using the function `get_ccf4(x, y, ...)`. \hh{XXX position is really the lag - i.e. we can compare lags across  different segments.}
A position is considered "good" if it results in a peak in the cross-correlation between the basis segment and the comparison.
<!-- the cross-correlation between the basis segment and the comparison is above a pre-defined threshold.  -->
The best registration position is decided upon using a multi-peak inspection with or without different segment lengths:

@@

dframe <- comparisons %>% select(-aligned, -cmps)

dframe$samesource <- with(dframe, bullet_to_land_predict(land1=landA, land2=landB, cmps_score, difference=1))

```

```{r, echo=FALSE}
dframe %>% ggplot(aes(x = landB, y = landA, fill = cmps_score)) + 
  geom_tile() + 
  geom_tile(aes(colour="same barrel"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
  scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6) + 
  scale_colour_manual("Source", values="darkorange") +
  facet_grid(bulletA ~ bulletB, labeller = "label_both") + xlab("Land B") + 
  ylab("Land A") + theme(aspect.ratio = 1) +
  geom_text(aes(label=cmps_score)) +
  theme_bw() +
  theme(aspect.ratio = 1)
```

@@

\begin{figure}
```{r segplot3, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
library(ggpubr)

ggarrange(
  plotlist = 
    unlist(seg.plot, 
           recursive = FALSE),
  ncol = 2, 
  nrow = 3)
```
\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all scales together. We are identifying five highest peaks at scale 1, three peaks at scale 2, and one peak at scale 3 since npeaks.set = c(5, 3, 1). Putting these plots together can help better understand why segment 6 is not a congruent matching profile segment. Here we can also see clearly that increasing segment length can reduce the number of false positive peaks.}
\end{figure}
